Data Mining in Nearby Galaxies

### 2016-07-04 main text/draft0.0.tex
Update draft0.0.tex
edits to abstract and affiliations. Added note re: keywords.

\begin{document}
\title{Data Mining in Nearby Galaxies}
\author[S. Rahmani, et. al.]{S.~Rahmani$^{1, 2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, E.~Peeters$^{1, 2, 4}$, P.~Barmby$^{1, 2}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
$^{4}$SETI Institute, 189 Bernardo Avenue, Suite 100, Mountain View, CA 94043, USA}
\maketitle

@@

\begin{abstract} 
Galaxies are very complex systems; therefore, a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties and various waveband data.
In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex big data.
We used one of these methods to study properties of nearby galaxies and create a more clear picture of them.
The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study data from M31 and M101. %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
%We studied 10 regions in M31 and 8 regions in M101. 
%These regions were chosen based on the availability of mid-infrared spectroscopy data.
%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
We created SOMs of various sizes and used them to extract information about the galaxies.
Using smaller-sized SOMs the data were clustered in 2 major groups; and for each group, we found correlations that could not have otherwise seen without clustering. 
In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
We then applied the SOMs that were generated from the M31 data to from M101. 
We found regions with similar properties in both galaxies placed in close regions in the SOMs.  
These results confirm that the generated SOMs can separate regions based on their physical properties, and can be used to make predictions for other regions in nearby galaxies or other targets. 
\end{abstract}
\begin{keywords} 
galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

>>>>

\begin{document}
\title{Data Mining in Nearby Galaxies}
\author[S. Rahmani, et. al.]{S.~Rahmani$^{1, 2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, E.~Peeters$^{1, 2, 4}$, P.~Barmby$^{1, 2}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
$^{4}$SETI Institute, 189 Bernardo Avenue, Suite 100, Mountain View, CA 94043, USA}
\maketitle

@@

\begin{abstract} 
Galaxies are very complex systems; a complete understanding of them cannot be achieved only from studying linear or logarithmic correlations between their properties.
The vast availability of data for nearby galaxies makes them suitable targets for exploratory data analysis. 
In the past few decades, a number of statistical methods have been developed and advanced to study and visualize complex datasets.
We used one of these methods to study the properties of nearby galaxies and create a clearer picture of them.
%Spatially resolved maps provide us with a unique view of the inside of galaxies. %and help better understand their properties.
In this project, we utilized the Kohonen Self Organizing Map (SOM) method to study observations of the nearby galaxies M31 and M101. %SOM is an unsupervised neural network for mapping and visualizing a complex and nonlinear high dimension data while preserving topological features of the original data. 
%We studied 10 regions in M31 and 8 regions in M101. 
%These regions were chosen based on the availability of mid-infrared spectroscopy data.
%For each region in M31, we had 46 data obtained through photometry, spectroscopy, and derived quantities (i.e., star formation rate, stellar mass, gas mass, etc.). 
%Using results from a correlation coefficient matrix, we reduced the dimension of this dataset and then trained the SOM using the new subset of data. 
We created SOMs of various sizes and used them to extract information about the galaxies.
Using smaller-sized SOMs, we found that the data were clustered in 2 major groups; for each group, we found correlations that could not have otherwise been seen without clustering. 
In the maps with larger sizes, we created networks to illustrate the relative relations of the regions with one another. 
We then applied the SOMs that were generated from the M31 data to data from M101 and 
found that regions with similar properties in both galaxies were placed in close regions in the SOMs.  
These results confirm that the generated SOMs can separate regions based on their physical properties and can be used to make predictions for other regions in nearby galaxies or other targets. 
\end{abstract}
\begin{keywords} %PB: I think MNRAS only lets you have up to 6 and they are supposed to be from here: http://journals.aas.org/authors/keywords2013.html
galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, data mining, methods:data analysis, techniques: image processing 
\end{keywords}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\import{../sections/}{intro0.0.tex}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
